High Resolution Identification of Protein-DNA Binding Events and Quality Control for ChIP-exo data

### 2015-11-17 rmarkdown/chip_exo_paper.Rnw
added section on strand imbalance

@@

%  We obtained esentially the same conclusion from the
% ChIP-exo data for CTCF factir from human sample Rhee and Pugh
% (\cite{exo1}) as well.

@@

>>>>

In order to asses the strand imbalance we create the following
visualization in figure \ref{fig:strand}. A) presents the FSR's
behaviour as lower depth regions are being filtered out. while B)
shows which percentage of the regions are composed by fragments of
both strand or only one. Roughly speaking in a lower quality dataset
there is going to be a higher amount of single stranded-regions. To
asses this, we divided the ChIP-exo regions into two sets, the oens
that overlap with a known set of peaks and the opposite and performed
$\chi^2$ tests.

\begin{figure}[h!]
  \centering  
  \includegraphics[width = .8\textwidth]{../figs/fsr/draft_fsr_plot.pdf}
  \includegraphics[width = .8\textwidth]{../figs/fsr/draft_label_prop_plot.pdf}
  \caption{ABCD}
  \label{fig:strand}
\end{figure}

@@

%  We obtained esentially the same conclusion from the
% ChIP-exo data for CTCF factor from human sample Rhee and Pugh
% (\cite{exo1}) as well.

@@

\section{Conclusions}
\label{sec:conclusions}
